### 2015-12-26 docs/ms_communitySynchrony.Rmd
updates discussion; adds mono vs polycutlture plot

### Effect of removing environmental stochasticity
For all five communities, removing environmental stochasticity cause synchrony of per capita growth rates to decrease, whether interspecific interactions were present or not (Fig. 3, top panels, blue tones vs. orange tones).
Without environmental stochasticity, synchrony of per capita growth rates all approximated the theoretical expectation of 1/S when only demographic stochasticity is operating (Fig. 3, top panels).
Again, no clear pattern emerges for the effect of removing environmental stochasticity on the synchrony of percent cover (Fig. 3, bottom panels).

@@

Discussion
----------
Temporal asynchrony among interacting populations can stabilize ecosystem-level function and is influenced by inter and intraspecific competition, demographic stochasticity, and environmental fluctuations.
We used multi-species population models applied to five semiarid plant communities to determine the relative influence of the drivers of community synchrony.
Our study produced three main findings that were consistent across all of our focal communities: (1) interspecific interactions had little impact on community synchrony because interspecific interactions were weak; (2) demographic stochasticity decreased community synchrony, as expected by theory, and its effect was largest in small populations; and (3) environmental fluctuations increased community synchrony since species-specific responses to the environment were positively, but not completely, correlated.
Thus, our results are in agreement with theoretical expectations: when species interactions and demographic stochasticity are weak, community synchrony approximately equals the synchrony of species' responses to the environment.

@@

### Environmental fluctuations drive community synchrony
In large populations where interspecific interactions are weak, synchrony is expected to be driven exclusively by environmental fluctuations.
Under such conditions community synchrony should approximately equal the synchrony of species' responses to the environment.
We find that environmental fluctuations drive synchrony of per capita growth rates and plant percent cover in all five communities.
Removing environmental fluctuations consistently reduced synchrony (Figs. 2,3) and the synchrony of species environmental responses was a strong predictor of community synchrony (Fig. 4).
This is unsurprising since we know that species interactions are weak in these communities.
More surprising is that our results appear to be quite general: across five arid-to-subhumid grasslands community synchrony is almost soley due to environmental fluctuations since interspecific interactions are weak.
Can we generalize our results to a vast majority of plant communities?

A recent analysis of several biodiversity-ecosystem function experiments suggests our results are anomolous.
@Gross2014 found that temporal asynchrony among plant species in four experiments was driven by interspecific competition that counteracted the synchronizing effect of environmental fluctuations.
However, their results are based on experimentally-assembled communities that have coexisted for less than 20 years.
Thus, community assembly processes that can result in competitive exclusion may yet to have been realized.
In contrast, the communities we studied consist of species that have coexisted for decades and have virtually zero niche overlap (@Chu2015).

@@

>>>>

### Effect of removing environmental stochasticity
For all five communities, removing environmental stochasticity cause synchrony of per capita growth rates to decrease, whether interspecific interactions were present or not (Fig. 3, top panels, blue tones vs. orange tones).
Without environmental stochasticity, synchrony of per capita growth rates all approximated the theoretical expectation of 1/S when only demographic stochasticity is operating (Fig. 3, top panels).
Again, no clear pattern emerges for the effect of removing environmental stochasticity on the synchrony of percent cover (Fig. 3, bottom panels).
Community-wide averages of vital rate random year effects are strong predictors of IPM-simulated synchrony of per capita growth rates ($\text{R}^2$ = 0.67; Fig. 4)

@@

Discussion
----------
Temporal asynchrony among interacting populations can stabilize ecosystem-level function and is influenced by inter and intraspecific competition, demographic stochasticity, and environmental fluctuations.
We used multi-species population models applied to five semiarid plant communities to determine the relative influence of the drivers of community synchrony.
Our study produced three main findings that were consistent across five plant communities: (1) interspecific interactions were weak and therefore had little impact on community synchrony; (2) demographic stochasticity decreased community synchrony, as expected by theory, and its effect was largest in small populations; and (3) environmental fluctuations increased community synchrony since species-specific responses to the environment were positively, but not completely, correlated.
Thus, our results are in agreement with theoretical expectations: when species interactions and demographic stochasticity are weak, community synchrony approximately equals the synchrony of species' responses to the environment.

@@

### Environmental fluctuations drive community synchrony
In large populations where interspecific interactions are weak, synchrony is expected to be driven exclusively by environmental fluctuations.
Under such conditions community synchrony should approximately equal the synchrony of species' responses to the environment.
We find that environmental fluctuations drive synchrony of per capita growth rates and plant percent cover in all five communities.
Removing environmental fluctuations consistently reduced synchrony (Fig. 3) and the synchrony of species environmental responses was a strong predictor of community synchrony ($\text{R}^2$ = 0.67; Fig. 4).
Likewise, removing interspecific interactions resulted in no discernable change in community synchrony of per capita growth rates (Fig. 2).
The lack of change indicates a strong correlation between species growing in polyculture (with interspecific interactions) and in monoculture (without interspecific interactions).
If we consider sychrony in monoculture to represent the synchrony of species' responses to the environment, then our results lead to only one conclusion: environmental fluctuations are the primary driver of community synchrony.
This is unsurprising since we know that species interactions are weak in these communities.
More surprising is that our results appear to be quite general: across five arid-to-subhumid grasslands community synchrony is almost soley due to environmental fluctuations since interspecific interactions are weak.
Can we generalize our results to a vast majority of plant communities?

A recent analysis of several biodiversity-ecosystem function experiments suggests our results are anomolous.
@Gross2014 found that temporal asynchrony among plant species in four experiments was driven by interspecific competition that counteracted the synchronizing effect of environmental fluctuations.
In fact, they found very weak correlations among species growin in polyculture and species growing in monoculture.
However, their results are based on experimentally-assembled communities that have coexisted for, at most, 11 years.
Thus, community assembly processes that can result in competitive exclusion may yet to have been realized and transient strong interspecific competition could be masking the synchronizing effects of the environment.
In contrast, the communities we studied consist of species that have coexisted for decades and have virtually zero niche overlap [@Chu2015].

@@

\begin{figure}[!ht]
  \centering
      \includegraphics{./components/envresp_vs_ipmsynch.png}
  \caption{Average synchrony of IPM-simulated per capita growth rates (from 13 year sections) as a function of the average synchrony of the vital rate random year effects for each site. Community sychrony is expected to approximately equal the synchrony of species' environmental responses in the absence of demographic stochasticity and strong interspecific interactions. The synchrony of species' random year effects across vital rates is a strong ($\text{R}^2$ = 0.67), but not perfect, predictor of community synchrony. Points are labeled by site codes: AZ = Arizona, ID = Idaho, KS = Kansas, MT = Montana, and NM = New Mexico.}
\end{figure}
